---
title: "Chronic Kidney Disease"
subtitle: "Group 4 Project"
author: "M. Vojtková, M. Hizanu, B. Zimoń, S. Rodopoulos"
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
date: '2022-05-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
install.packages("png")
library(png)
```

## Introduction



## Materials and Methods 

- Cleaning and augmenting
- Data exploration
- Data analysis
- Modelling

## Materials and Methods | The Dataset
- Dataset was obtained from UCI Machine Learning Depository
- 400 observations of 25 attributes: 

<div class="columns-2">
  
-  age
- blood pressure
- specific gravity
- albumin
- sugar
- red blood cells
- pus cell
- pus cell clumps
- bacteria
- blood glucose random
- blood urea
- serum creatinine
- sodium
- potassium
- hemoglobin
- packed cell volume
- white blood cell count
- red blood cell count
- hypertension
- diabetes mellitus
- coronary artery disease
- appetite
- pedal edema
- anemia
- class

</div>

## Data loading, cleaning and augmentation

- insert progress plot here
- missing values plot
- specify added variables

## Data exploration

```{r}

img<-readPNG("figures/distributions/age_distribution.png")

```


- ckd and not ckd distrb
- disease association ??
- hemo_pcv association + red_blood
- hemoglobin and albumin
- relationship blood urea serum creatine -> biological meaning

- Corellation heatmap -> take out age_group and disease no


## Data analysis | PCA and K-nearest neighbours

## Modelling | Linear regression and Finding the most optimal model

## Results

```{r cars, echo = TRUE}
summary(cars)
```

## Discussion

```{r pressure}
plot(pressure)
```

